---
title: "Triage Analysis"
output: html_document
---

The code below organizes the data and generates a few necessary variables.


```{r}
# Load Triage Data
load("./data/upstream-inputs/triage-dataset-non-sensitive.Rdata")

# Libraries
library(stargazer)

# Output some constants
# Function to save constants
save_constant <- function(x, file_name) {
  write(x, file = paste0("./output/constants/", file_name, ".txt"))
}

# triage-n-observations
save_constant(nrow(triage_dataset_non_sensitive), "triage-n-observations")
# triage-n-implemented
x <-
  equals(triage_dataset_non_sensitive$phase_2_decision, "Approved") %>%
  sum(na.rm = TRUE)
save_constant(x, "triage-n-implemented")

# Some data cleaning
triage_dataset_non_sensitive$phase_2_decision <- NULL
# Convert online metric deltas from fraction to percent
triage_dataset_non_sensitive %<>% mutate(
  `delta session success rate` = 100 * `delta session success rate`,
  `delta sessions per unique user` = 100 * `delta sessions per unique user`,
  `delta time to success` = 100 * `delta time to success`
)

# Simplify names
names(triage_dataset_non_sensitive) <- gsub("phase_1_sbs_do", "off1", names(triage_dataset_non_sensitive))
names(triage_dataset_non_sensitive) <- gsub("phase_1_sbs_dt", "off2", names(triage_dataset_non_sensitive))
names(triage_dataset_non_sensitive) <- gsub("phase_1_xdcg_do", "off3", names(triage_dataset_non_sensitive))
names(triage_dataset_non_sensitive) <- gsub("phase_1_xdcg_dt", "off4", names(triage_dataset_non_sensitive))

names(triage_dataset_non_sensitive) <- gsub("delta sessions per unique user", "on1", names(triage_dataset_non_sensitive))
names(triage_dataset_non_sensitive) <- gsub("delta session success rate", "on2", names(triage_dataset_non_sensitive))
names(triage_dataset_non_sensitive) <- gsub("delta time to success", "on3", names(triage_dataset_non_sensitive))
names(triage_dataset_non_sensitive) <- gsub("p-value sessions per unique user", "on1_pv", names(triage_dataset_non_sensitive))
names(triage_dataset_non_sensitive) <- gsub("p-value session success rate", "on2_pv", names(triage_dataset_non_sensitive))
names(triage_dataset_non_sensitive) <- gsub("p-value time to success", "on3_pv", names(triage_dataset_non_sensitive))

triage_dataset_non_sensitive$phase_1_decision[triage_dataset_non_sensitive$phase_1_decision == "Return to Phase 1"] <- "Return"
triage_dataset_non_sensitive$phase_1_decision[is.na(triage_dataset_non_sensitive$phase_1_decision)] <- "Success"

# Create t-stats and standard deviations each offline metric
for(i in 1:4){
  met <- paste("off",i,sep="")
  pv <- paste(met,"_p_value",sep="")
  t <- paste(met,"_t",sep="")
  std <- paste(met,"_std",sep="")
  nn <- paste(met,"_n",sep="")
  y <- data.matrix(triage_dataset_non_sensitive[ , c(met)])
  y_pv <- data.matrix(triage_dataset_non_sensitive[ , c(pv)])
  y_n <- data.matrix(triage_dataset_non_sensitive[ , c(nn)])
  y_t <- data.matrix(qnorm(1-(y_pv/2))*((y > 0) - (y < 0)))
  triage_dataset_non_sensitive[ , c(t)] <- data.frame(y_t)
  triage_dataset_non_sensitive[ , c(std)] <- data.frame((sqrt(y_n)*y)/y_t)
}

# Create minimum across t-stats of offline metrics 
triage_dataset_non_sensitive <- transform(triage_dataset_non_sensitive, minoff = pmin(triage_dataset_non_sensitive$off1_t, triage_dataset_non_sensitive$off2_t, triage_dataset_non_sensitive$off3_t, triage_dataset_non_sensitive$off4_t))

# Create mean across t-stats of offline metrics 
triage_dataset_non_sensitive$meanoff <- rowMeans(triage_dataset_non_sensitive[,c("off1_t", "off2_t", "off3_t", "off4_t")], na.rm = FALSE)

```


##Offline Analysis

First, I plot the histogram of the t-statistic of the offline metrics to show that unsuccesful experiments are not kept in the dataset. 

```{r}

# Gen Histogram data

hdata <- rbind( 
  data.frame(V1 = triage_dataset_non_sensitive[,c("off1_t")], type = "All"), 
  data.frame(V1 = triage_dataset_non_sensitive$off1_t[triage_dataset_non_sensitive$phase_1_decision == "Success"], type = "Success")
)

hdata[, c("met")] <- "#1" 


for(i in 2:4){
  met <- paste("off",i,sep="")
  name <- paste("#",i,sep="")
  t <- paste(met,"_t",sep="")
  y <- triage_dataset_non_sensitive[,c(t)]
  
  aux <- rbind( 
    data.frame(V1 = y, type = "All"), 
    data.frame(V1 = y[triage_dataset_non_sensitive$phase_1_decision == "Success"], type = "Success")
  )
  
  aux[, c("met")] <- name 
  
  j <- i + 1
  
  hdata <- rbind(hdata,aux)
  
  rm(aux)
  
}

# Gen Simple Histogram

pp <- ggplot(hdata,aes(x=V1)) + 
  geom_histogram(dat=subset(hdata,type == "All"),aes(fill=type), col=I("black"), alpha = 0.6, bins = 8) +
  labs(title="T-Stats Offline Metrics", x="t-stat") +
  xlim(c(-4,4)) +
  ylim(c(0,10)) + facet_wrap( ~ met, ncol=2)
ggsave(file = "./output/figures/histogram-off.pdf", pp)
pp

# Gen Simple Histogram, pooled metrics (goes in the paper)
pp <- ggplot(hdata,aes(x=V1)) + 
  geom_histogram(dat=subset(hdata,type == "All"), bins = 8) +
  labs(x="t-stat") +
  xlim(c(-4,4))
ggsave(file = "./output/figures/histogram-pooled-offline-metrics.pdf", pp)
pp

# Overlapped Histograms
qq <- ggplot(hdata,aes(x=V1)) + 
  geom_histogram(dat=subset(hdata,type == "All"),aes(fill=type), col=I("black"), alpha = 0.6, bins = 8) +
  geom_histogram(dat=subset(hdata,type == "Success"),aes(fill=type), alpha = 0.8, bins = 8) +
  labs(title="T-Stats Offline Metrics", x="t-stat") +
  scale_fill_manual(name="", values=c("white","blue"),labels=c("All","Success")) +
  xlim(c(-4,4)) +
  ylim(c(0,10)) + facet_wrap( ~ met, ncol=2)
ggsave(file = "./output/figures/histogram-offcombined.pdf", qq)
qq

# Overlapped Histogram of all metrics together
qq <- ggplot(hdata,aes(x=V1)) + 
  geom_histogram(dat=subset(hdata,type == "All"),aes(fill=type), col=I("black"), alpha = 0.6, bins = 8) +
  geom_histogram(dat=subset(hdata,type == "Success"),aes(fill=type), alpha = 0.8, bins = 8) +
  labs(title="Pooled T-Stats Offline Metrics", x="t-stat") +
  scale_fill_manual(name="", values=c("white","blue"),labels=c("All","Success")) +
  xlim(c(-4,4))
ggsave(file = "./output/figures/histogram-pooloff.pdf", qq)
qq

# Overlapped Histogram of the minimum value of the metric

mindata <- rbind( 
  data.frame(V1 = triage_dataset_non_sensitive[,c("minoff")], type = "All"), 
  data.frame(V1 = triage_dataset_non_sensitive$minoff[triage_dataset_non_sensitive$phase_1_decision == "Success"], type = "Success")
)

ww <- ggplot(mindata,aes(x=V1)) + 
  geom_histogram(dat=subset(mindata,type == "All"),aes(fill=type), col=I("black"), alpha = 0.6, bins = 12) +
  geom_histogram(dat=subset(mindata,type == "Success"),aes(fill=type), alpha = 0.8, bins = 12) +
  labs(title="Minimum T-Stat Across Offline Metrics", x="t-stat") +
  scale_fill_manual(name="", values=c("white","blue"),labels=c("All","Success")) +
  xlim(c(-4,4)) +
  ylim(c(0,10))
ggsave(file = "./output/figures/histogram-offmin.pdf", ww)
ww

```

Second, I plot the t-stats of the offline metrics to check if they are correlated

```{r}

# Create and export scatter plots of t-stats of offline metrics

s1 <- ggplot(triage_dataset_non_sensitive, aes(x=off1_t, y=off2_t)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Metric #1", y = "Metric #2")
s2 <- ggplot(triage_dataset_non_sensitive, aes(x=off1_t, y=off3_t)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Metric #1", y = "Metric #3")
s3 <- ggplot(triage_dataset_non_sensitive, aes(x=off1_t, y=off4_t)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Metric #1", y = "Metric #4")
s4 <- ggplot(triage_dataset_non_sensitive, aes(x=off2_t, y=off3_t)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Metric #2", y = "Metric #3")
s5 <- ggplot(triage_dataset_non_sensitive, aes(x=off2_t, y=off4_t)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Metric #2", y = "Metric #4")
s6 <- ggplot(triage_dataset_non_sensitive, aes(x=off3_t, y=off4_t)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Metric #3", y = "Metric #4")

ss <- grid.arrange(s1, s2, s3, s4, ncol=2, nrow = 2)
ss
ggsave("./output/figures/soff-simple.pdf", ss)
ss <- grid.arrange(s1, s2, s3, s4, s5, s6, ncol=3, nrow = 2)
ss
ggsave("./output/figures/offline-metrics-scatter-matrix.pdf", ss)

```

I complement this with a correlation matrix of the offline metrics t-stats

```{r}

# Correlation between offline metrics 

cor(triage_dataset_non_sensitive[,c("off1","off2","off3","off4")], use = "complete.obs")

```

##Online - Offline Analysis

In this section I explore the relation between the offline metrics and the SSR. First, I do a scatter plot of the SSR as a function of the offline metrics.

```{r}

### Offline & Online Analysis ###
  
# Scatter plot of offline and SSR (this is the only figure we will have in the paper. The rest put in the appendix)

s1 <- ggplot(triage_dataset_non_sensitive, aes(x=off1_t, y=on2)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Offline metric #1", y = "Delta in success rate") +
  theme_bw()
s2 <- ggplot(triage_dataset_non_sensitive, aes(x=off2_t, y=on2)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Offline metric #2", y = "Delta in success rate") +
  theme_bw()
s3 <- ggplot(triage_dataset_non_sensitive, aes(x=off3_t, y=on2)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Offline metric #3", y = "Delta in success rate") +
  theme_bw()
s4 <- ggplot(triage_dataset_non_sensitive, aes(x=off4_t, y=on2)) + geom_point(size=2, color = "black", fill = "black",shape=19, alpha = 0.8) + labs(x="Offline metric #4", y = "Delta in success rate") +
  theme_bw()

ss <- grid.arrange(s1, s2, s3, s4, ncol=2, nrow = 2)
ss
ggsave("./output/figures/ssr-vs-offline-metrics.pdf", ss)

# Regression table
df <- triage_dataset_non_sensitive %>%
  transmute(`Delta in success rate` = on2,
            `offline metric 1` = off1_t,
            `offline metric 2` = off2_t,
            `offline metric 3` = off3_t,
            `offline metric 4` = off4_t)

lm(`Delta in success rate` ~ ., data = df) %>%
  stargazer(out = "./output/tables/ssr-vs-offline-regression.tex",
            float = FALSE,
            dep.var.labels   = "Measured Delta in success rate",
            covariate.labels = c("Offline metric 1", "Offline metric 2",
                                 "Offline metric 3", "Offline metric 4"))

```

Finally, I present a bar graph of the average SSR for experiments below and above a median offline metric. 

```{r}

# Bar graph of SSR for above and below median experiments in offline metrics


off_med <- median(triage_dataset_non_sensitive[,c("off1_t")], na.rm  =  TRUE)
triage_dataset_non_sensitive[ , c("off1_d")] <- (triage_dataset_non_sensitive[,c("off1_t")] > off_med)

myData <- aggregate(triage_dataset_non_sensitive[,c("on2")],
                    by = list(cyl = triage_dataset_non_sensitive[,c("off1_d")]),
                    FUN = function(x) c(mean = mean(x, na.rm = TRUE), sd = sd(x, na.rm = TRUE),
                                        n = length(x)))
myData <- do.call(data.frame, myData)
myData$se <- myData$x.sd / sqrt(myData$x.n)

colnames(myData) <- c("cyl", "mean", "sd", "n", "se")

myData$Group <- c("Below median","Above median")

myData$met <- "Metric #1"

for(i in 2:4){
  met <- paste("off",i,sep="")
  name <- paste("Metric #",i,sep="")
  t <- paste(met,"_t",sep="")
  d <- paste(met,"_d",sep="")
  y <- triage_dataset_non_sensitive[,c(t)]
  
  off_med <- median(triage_dataset_non_sensitive[,c(t)], na.rm  =  TRUE)
  triage_dataset_non_sensitive[ , c(d)] <- (triage_dataset_non_sensitive[,c(t)] > off_med)
  
  aux <- aggregate(triage_dataset_non_sensitive[,c("on2")],
                      by = list(cyl = triage_dataset_non_sensitive[,c(d)]),
                      FUN = function(x) c(mean = mean(x, na.rm = TRUE), sd = sd(x, na.rm = TRUE),
                                          n = length(x)))
  aux <- do.call(data.frame, aux)
  aux$se <- aux$x.sd / sqrt(aux$x.n)
  
  colnames(aux) <- c("cyl", "mean", "sd", "n", "se")
  
  aux$Group <- c("Below median","Above median")
  
  aux[, c("met")] <- name 
  
  myData <- rbind(myData,aux)
  
  rm(aux)
  
}

ss <- ggplot(myData, aes(x=met, y=mean, fill=Group)) + 
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                position=position_dodge(.9)) + labs(x="Offline metrics", y = "Measured Delta in success rate")

ss
ggsave("./output/figures/session-success-versus-offline-bar.pdf", ss)

```


